Enhance Road Detection Data Processing of LiDAR Point Clouds to Specifically Identify Unmarked Gravel Rural Roads

### 2023-02-20 Huston_Paper.tex
Updates

	{Random Decision Forests were created using MATLAB's $TreeBagger$ function, which creates an ensemble of bagged decision trees. Included features, tree depth, and number of trees were principal guiding factors in RDF creation. Tree depth was determined by examination of the validation accuracy to determine a point of diminishing returns. Point cloud translation and rotation was accomplished using transformation matrices derived from GPS and IMU data.}

%		{Rotation matrices were created using extracted roll, pitch, and yaw data from the IMU. LiDAR origin was found using GPS longitude, latitude, and altitude data. Physical distances between the GPS, IMU, and LiDAR was rectitude by obtaining reference frames provided by AutonomouStuff. GPS coordinates were offset by the current orientation and converts the ground truth to the LiDAR frame. GPS, IMU, and LiDAR reference frames and rotational updates were combined into trajectory vectors. Consecutive point cloud scans may then translated and rotated with derived transformation matrices (Figure \ref{fig:Compiled_PCD}).}

	{Validation error was used as the primary means to compare RDF performance. MATLAB was used to load verification data and test increasing sizes of RDF algorithms for accuracy by comparing the known data types against the RDF result. RANSAC versus MLS was tested using identical feature sets (Figures \ref{fig:all_mls_ransac_comp} \ref{fig:xyz_mls_ransac_comp}). Validation error plots were used to influence feature sets and depth in later iterations of RDFs. Number of trees in the RDF verses error allowed for determination of an early stopping point for algorithm growth (Figure \ref{fig:mls_zxy_early_stopping}) by choosing the point where the change in moving average did not exceed 10\% and was within 15\% of the minimum error.}

@@

>>>>

	{Random Decision Forests were created using MATLAB's $TreeBagger$ function, which creates an ensemble of bagged decision trees. Included features, tree depth, and number of trees were principal guiding factors in RDF creation. Validation error was used as the primary means to compare RDF performance. MATLAB was used to load verification data and test increasing sizes of RDF algorithms for accuracy by comparing the known data types against the RDF result. RANSAC versus MLS was tested using identical feature sets (Figures \ref{fig:all_mls_ransac_comp} \ref{fig:xyz_mls_ransac_comp}). Number of trees in the RDF verses error allowed for determination of an early stopping point for algorithm growth (Figure \ref{fig:mls_zxy_early_stopping}) by choosing the point where the change in moving average did not exceed 10\% and was within 15\% of the minimum error.}

@@

	{Testing consecutive scans required a method of compiling LiDAR data into a single point cloud and manually classifying areas for . Six stretches of unmarked roads was gathered for this work. }

	%		{Point cloud translation and rotation was accomplished using transformation matrices derived from GPS and IMU data. Rotation matrices were created using extracted roll, pitch, and yaw data from the IMU. LiDAR origin was found using GPS longitude, latitude, and altitude data. Physical distances between the GPS, IMU, and LiDAR was rectitude by obtaining reference frames provided by AutonomouStuff. GPS coordinates were offset by the current orientation and converts the ground truth to the LiDAR frame. GPS, IMU, and LiDAR reference frames and rotational updates were combined into trajectory vectors. Consecutive point cloud scans may then translated and rotated with derived transformation matrices (Figure \ref{fig:Compiled_PCD}).}

	{Testing consecutive scans was completed by post processing rosbags that contained scanning LiDAR, GPS, and IMU data of an unmarked road. Physical distance between the GPS, IMU, and LiDAR were rectified by measuring the distance between the modules. Rotational reference frames between the GPS, IMU, and LiDAR were rectified by applying appropriate rotational matrices. Transformation matrices were created by considering the GPS position and the IMU's roll, pitch, and yaw data. Point cloud data was then classified using one of the generated RDF algorithms. Translation and rotation was applied to the terrain classification results with the closest matching transformation matrices (Figure \ref{fig:Classified_PointCloud_1_ALL}). Comparing averaged X, Y, and Z coordinates of classified quadrant (Figure \ref{fig:Classified_PointCloud_1_AVG}) allowed for easier comparison and scoring of the RDF classification to the manually classified areas. Consecutive scanning LiDAR data was compiled allowing for manually assigning areas representing road or side of road surfaces (Figure \ref{fig:Manually_Classified_Areas}). Side of road area were manually defined as an area roughly one meter outwards from the road edge for consideration of road edge detection. Per-Quadrant classification rate data was gathered and plotted, the average rate being 2.97 quadrants per second (Figure \ref{fig:Time_Hz_Rate}). This was tested with a machine with 64 GB of DDR4 RAM and a Ryzen 9 5900X 12 core x 24 thread CPU.}
